\section{Conclusions and Outlook}
\label{sec:conclusions-outlook}

We have presented an approach to automatically extract mode diagrams from the so far purely textual Blech language.
The stateful nature of Blech allowed for a natural mapping from Blech code to modes/states and transitions.
We postulate that such a translation would also be natural for other textual languages for developing reactive systems.

The mode diagrams are effectively a slightly extended and abstracted variant of \acp{scchart}. This choice made it simple to capture precisely the semantics of the state-relevant part of the Blech language, which is not surprising given that Blech was inspired by the sequentially-constructive model of computation realized in \acp{scchart}~\cite{GretzG18}.
Furthermore, we could harness the existing open-source infrastructure for \acp{scchart} to create the mode diagrams, crucially including the ability to automatically compute a layout for them.

The preliminary feedback from industrial users was encouraging, but also pointed to a number of still open questions and issues.
The users also confirmed that preferences on mode diagrams are quite individual.
Thus, flexibility and configurability for the mode diagram synthesis seems key.
This may also include, as part of possible future work, the ability to choose how much ``semantic accuracy'' the mode diagrams should provide.
Our focus so far was to provide a diagram synthesis that abstracted from run-time behavior in particular concerning data handling, but that still precisely captured possible state traces in reactions.
That goal implied the need to differentiate, \eg, between immediate and delayed transitions and between different types of abort.
However, at least for some users that was still too much detail, and made the mode diagrams less obvious to understand than a plain state diagram with just one type of transition would have been.

Another possible improvement, also according to the feedback from the industrial users, would be the merge of awaiting transitions followed by a decision point (\ie if-else, repeat-until). That merge is not trivial regarding the triggers on the transitions. If one would simply merge the triggers from the delayed transition with the branches of the if-else, the label of the \lstinline{await} would be duplicated. It is doubtful that this is an optimal and compact solution. Further problems arise if variables are used in the if-else conditions and the \lstinline{await} statement. Complicated conditions might emerge this way. Boolean optimizations and smart simplifications have to be made here to make the merge viable.

On a practical implementation side, a full integration into Visual Studio Code would allow for example to link the elements in the code with their visual representation, as is already the case in \ac{kieler} when working with textual \acp{scchart} and their visualization.
Clicking in the visualization could highlight the corresponding parts in the code and vice versa, a feature that several industrial users had asked for.
